Even-point Multi-loop Unitarity and its Applications: Exponentiation, Anomalies and Evanescence

### 2023-07-29 eventPointTwoLoop.tex

As we have shown, carrying out such sYM recycled cut verifications of \eqn{eq:N42bub} and \eqn{eq:N4ostrich} in the case of maximally supersymmetric Yang-Mills in four-dimensions is trivial -- only one (non-vanishing) diagram contributes to each cut.

>>>>

Carrying out such sYM recycled cut verifications of \eqn{eq:N42bub} and \eqn{eq:N4ostrich} in the case of maximally supersymmetric Yang-Mills in four-dimensions is straightforward -- only one (non-vanishing) diagram contributes to each cut. We provide the details in an appendix which may be of pedagogic interest.
